### 2021-02-22 newvariant.tex
discussion

>>>>

We argue that both perspectives (i.e., whether we hold relative strength or speed constant) are useful in understanding the dynamics of the new variant.
Early in the spread, we typically want to fix the relative speed because we can directly observe it.
As more information about the transmission and immunity profiles of the new variant becomes available, it is better to fix the relative strength as it better mathces biological assumptions.
We suggest researchers to be mindful about which quantity they hold constant and how their assumptions lead to their conclusions.

Our simple framework further reveals counterintuitive, but important, insight.
In general, one would expect that stronger intervention strategies is required in order to slow down the replacement of the original strain by the new variant.
However, this is only true if both have the same mean generation intervals (\fref{relspeed}B).
If the new variant has longer generation intervals than the original strain, imposing strong intervention (therefore reducing both $\RR_w$ and $\RR_v$ by a constant amount) results in a higher relative speed $\delta$, and therefore faster replacement of the original strain (\fref{relspeed}A).

Since the beginning of the SARS-CoV-2 pandemic, the importance of understanding the role of generation-interval distributions in its spread has been constantly emphasized.
Yet, we still feel that generation intervals are under-appreciated, often viewed as a leeway to estimating $\RR$.
Future studies should consider the possibility that the new variant might have longer generation intervals and evaluate how assumptions about generation intervals affect their conclusions.
